\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-08-22 paper.tex
removed mentions of unmodified as this is wrong
added akash and paul (need to somehow fix the author names)
switched to the USENIX style

% This is "sig-alternate.tex" V2.0 May 2012
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate}

@@

\begin{document}
%
% --- Author Metadata here ---
\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Uncovering Distributed System Bugs\\ during Testing (not Production!)}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{6} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor Pantazis Deligiannis\\
       \affaddr{Imperial College London}\\
       \affaddr{London, UK}\\
       \email{p.deligiannis@imperial.ac.uk}
% 2nd. author
\alignauthor John Erickson\\
       \affaddr{Microsoft}\\
       \affaddr{Redmond, WA, USA}\\
       \email{jerick@microsoft.com}
% 3rd. author
\alignauthor Cheng Huang\\
       \affaddr{Microsoft Research}\\
       \affaddr{Redmond, WA, USA}\\
       \email{cheng.huang@microsoft.com}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor Matt McCutchen\\
       \affaddr{MIT}\\
       \affaddr{Cambridge, MA, USA}\\
       \email{rmccutch@mit.edu}
% 5th. author
\alignauthor Shaz Qadeer\\
       \affaddr{Microsoft Research}\\
       \affaddr{Redmond, WA, USA}\\
       \email{qadeer@microsoft.com}
% 6th. author
\alignauthor Wolfram Schulte\\
       \affaddr{Microsoft}\\
       \affaddr{Redmond, WA, USA}\\
       \email{schulte@microsoft.com}
}

\date{17 August 2015}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
Testing distributed systems is very challenging due to multiple sources of nondeterminism, such as arbitrary interleavings between event handlers and unexpected node failures. Stress testing, commonly used in industry today, is unable to deal with this kind of nondeterminism, which results in the most tricky bugs being missed during testing and only getting exposed in production.

We present a new methodology for systematically testing unmodified distributed systems. Our approach involves the use of \psharp, an extension of \csharp that combines a flexible environmental modeling approach with a concurrency testing framework, which can capture and systematically explore all sources of nondeterminism. We present two case studies of using \psharp to test production distributed systems inside Microsoft. Using \psharp, we managed to uncover a very subtle bug that was haunting developers for a long time, as they did not have an effective way to reproduce it. \psharp uncovered the bug in a very small setting, which made it easy to examine traces, identify and fix the problem.

\end{abstract}

\category{D.2.4}{Software Engineering}{Software/Program Verification}
\category{D.2.5}{Software Engineering}{Testing and Debugging}

\keywords{distributed systems, testing}

@@

%\section{Acknowledgments}
%Draft.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{references}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns

>>>>

% TEMPLATE for Usenix papers, specifically to meet requirements of
%  USENIX '05
% originally a template for producing IEEE-format articles using LaTeX.
%   written by Matthew Ward, CS Department, Worcester Polytechnic Institute.
% adapted by David Beazley for his excellent SWIG paper in Proceedings,
%   Tcl 96
% turned into a smartass generic template by De Clarke, with thanks to
%   both the above pioneers
% use at your own risk.  Complaints to /dev/null.
% make it two column with no page numbering, default is 10 point

% Munged by Fred Douglis <douglis@research.att.com> 10/97 to separate
% the .sty file from the LaTeX source template, so that people can
% more easily include the .sty file into an existing document.  Also
% changed to more closely follow the style guidelines as represented
% by the Word sample file.

% Note that since 2010, USENIX does not require endnotes. If you want
% foot of page notes, don't include the endnotes package in the 
% usepackage command, below.

% This version uses the latex2e styles, not the very ancient 2.09 stuff.
\documentclass[letterpaper,twocolumn,10pt]{article}

\usepackage{usenix,epsfig,endnotes}

@@

\begin{document}

%don't want date printed
\date{}

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)}

%for single author (just remove % characters)
\author{
{\rm Pantazis Deligiannis$^1$, John Erickson$^2$, Cheng Huang$^3$, Akash Lal$^3$}\\
{\rm Matt McCutchen$^4$, Shaz Qadeer$^3$, Wolfram Schulte$^2$, Paul Thomson$^1$}\\\\
$^1$Imperial College London, $^2$Microsoft, $^3$Microsoft Research, $^4$MIT
} % end author

\maketitle

% Use the following at camera-ready time to suppress page numbers.
% Comment it out when you first submit the paper for review.
\thispagestyle{empty}

\subsection*{Abstract}
Testing distributed systems is very challenging due to multiple sources of nondeterminism, such as arbitrary interleavings between event handlers and unexpected node failures. Stress testing, commonly used in industry today, is unable to deal with this kind of nondeterminism, which results in the most tricky bugs being missed during testing and only getting exposed in production.

We present a new methodology for systematically testing distributed systems. Our approach involves the use of \psharp, an extension of \csharp that combines a flexible environmental modeling approach with a concurrency testing framework, which can capture and systematically explore all sources of nondeterminism. We present two case studies of using \psharp to test production distributed systems inside Microsoft. Using \psharp, we managed to uncover a very subtle bug that was haunting developers for a long time, as they did not have an effective way to reproduce it. \psharp uncovered the bug in a very small setting, which made it easy to examine traces, identify and fix the problem.

@@

\section{Acknowledgments}

A polite author always includes acknowledgments.  Thank everyone,
especially those who funded the work.

\section{Availability}

It's great when this section says that MyWonderfulApp is free software, 
available via anonymous FTP from ... Also, it's even greater when you can
write that information is also  available on the Wonderful homepage at

{\footnotesize \bibliographystyle{acm}
\bibliography{references}}
